Towards Verifying the Bitcoin-S Library

### 2019-06-22 paper/paper.tex
add code about propagate require

Corresponding code:

\begin{lstlisting}[style=scala]
sealed abstract class Number {
  /** The underlying scala number used to to hold the number */
  protected def underlying: BigInt

@@

>>>>

Corresponding code:
\begin{lstlisting}[style=scala]
sealed abstract class Number {
  /** The underlying scala number used to to hold the number */
  protected def underlying: BigInt

@@

Code after:
\begin{lstlisting}[style=scala]
sealed abstract class Number {
  /** The underlying scala number used to to hold the number */
  protected def underlying: BigInt

  def +(num: Int64): Int64 = {
    require(
          num == Int64.zero
      && this.underlying <= BigInt("9223372036854775807")
      && this.underlying >= BigInt("-9223372036854775808"))
    apply(checkResult(underlying + num.underlying))
  }

The same problem occurs in the Int64 constructor.

Before:
\begin{lstlisting}[style=scala]
sealed abstract class Int64 extends SignedNumber {
  override def apply: BigInt => Int64 = Int64(_)
}

case object Int64 extends BaseNumbers[Int64] {
  lazy val zero = Int64(0)
  lazy val one = Int64(1)

private case class Int64Impl(underlying: BigInt) extends Int64 {
  require(underlying >= BigInt("-9223372036854775808"))
  require(underlying <= BigInt("9223372036854775807"))
}
\end{lstlisting}

After:
\begin{lstlisting}[style=scala]
sealed abstract class Int64 extends SignedNumber {
  override def apply: BigInt => Int64 = bigInt => {
    require(
          bigInt >= BigInt("-9223372036854775808")
      && bigInt <= BigInt("9223372036854775807"))

    Int64(bigInt)
  }
}

case object Int64 extends BaseNumbers[Int64] {
  lazy val zero = Int64(0)
  lazy val one = Int64(1)

  def apply(bigInt: BigInt): Int64 = {
    require(
         bigInt >= BigInt("-9223372036854775808")
      && bigInt <= BigInt("9223372036854775807"))

    Int64Impl(bigInt)
  }
}

private case class Int64Impl(underlying: BigInt) extends Int64 {
  require(underlying >= BigInt("-9223372036854775808"))
  require(underlying <= BigInt("9223372036854775807"))
}
\end{lstlisting}
